\vskip-0.6in \Large Political Uncertainty

### 2015-12-16 GS-extension.tex
add a bit of intuition about see-saw
fill in central numerical example of al = 0

@@

>>>>

\vskip.2in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Imagine a see-saw; these guys are weights on the see-saw.
\end{itemize}

@@

		\vskip.5in
Going to explore in-depth case of $\al = 0.0$	\\
	\begin{tabular}{crrrrr}
			            & -0.5 & 0.0 						& 0.5\\
			up to WB=7	&	0	&		0					 &	0 \\		
			WB = 8    & 	0&  some &	0	\\
			WB = 9   & 	some & some + .5 &	0	\\
			WB = 10 to 20 & some & some + .5 & some + 1
	\end{tabular}
